\documentclass[a4paper]{resume}
\usepackage{hyperref, enumitem}

\input{glyphtounicode}
\pdfgentounicode=1

\begin{document}
\vspace*{-20pt}

\setlist[itemize]{leftmargin=*}
\pagenumbering{gobble}

%Name, Email, Linkedin, Github, Website
\profile{Omshi Samal}{samal.omshi@gmail.com}{linkedin.com/in/omshi}{github.com/omshii}{omshi.me}

\vspace{10pt}

\resection{Education}
\resubsection{Colgate University}{Expected Graduation: Spring 2024}
\begin{itemize} \vspace{-5pt} \itemsep -2pt
	\item B.A. Computer Science and Math
	\item GPA: 3.76/4.00
	\item Relevant coursework: Introduction to Computer Systems, Calculus III, Systems Biology, Discrete Structures, Linear Algebra
\end{itemize}
\enresection

\vspace{-2pt}

\resection{Technical Skills}
\textbf{Languages:} Java, Python, MATLAB, C, C++, SQL, HTML, CSS \\
\textbf{Tools and Libraries:} Git, Docker, Numpy, Pandas, LaTeX, Android
\enresection

\vspace{3pt}

\resection{Technical Experience}
\resubsection{Computer Science Research Assistant, Gember-Jacobson Lab, Colgate University}{Dec 2020 - Present}
\begin{itemize} \vspace{-5pt} \itemsep -2pt
	\item Analyzing common bugs in open source routing software, using Python and Docker to simulate router and networking environments. 
\end{itemize}
\enresubsection
\resubsection{Computational Biology Research Assistant, AyLab, Colgate University}{Dec 2020 - Present}
\begin{itemize} \vspace{-5pt} \itemsep -2pt
	\item Researching noise propagation in cellular signaling networks, using MATLAB to develop and run stochastic simulations of computational models. 
\end{itemize}
\enresubsection
\resubsection{Freelance Developer and Designer, Multiple Companies}{Dec 2019 - Apr 2020}
\begin{itemize} \vspace{-5pt} \itemsep -2pt
	\item Designed websites, logos, and other branding materials and wrote scripts for automation and analytics.
	\item Increased user engagement and leads by adding custom invite pages, interactive forms, blogs, and other design tweaks, using WordPress and PHP.
\end{itemize}
\enresubsection
\resubsection{Intern, Odisha Crafts Museum}{Aug 2019 - Oct 2019}
\begin{itemize} \vspace{-5pt} \itemsep -2pt
	\item Created an audio tour system to increase visitor access to information, used Audacity for audio processing and SoundCloud API for hosting the tour.
	\item Saved 4+ weeks by writing scripts using Python to automate the online archival process.
	\item Revamped the museum website using Adobe XD and Illustrator focusing on classic design principles.
\end{itemize}
\enresubsection
\resubsection{Open Source Contributor, Liquid Galaxy LAB}{Oct 2017 - Dec 2019}
\begin{itemize} \vspace{-5pt} \itemsep -2pt
	\item Created a Google Assistant app to control the Google Earth application by voice, using Dialogflow and Nodejs.
	\item Developed Python and Bash scripts, shipped Docker environments, and created paired Android apps to transmit information via Bluetooth.
	\item Mentored for Liquid Galaxy Lab as a part of Google Code-In 2018 and 2019 - created programming tasks and moderated a community of 500+ students.
\end{itemize}
\enresection

\resection{Independent Technical Projects}
\resubsection{pykitables \hspace*{10pt} \href{https://github.com/omshii/pykitables}{github.com/omshii/pykitables}}{}
\begin{itemize} \vspace{-5pt} \itemsep -2pt
	\item Developed a Python package to cleanly scrape tables from Wikipedia for data analysis. 
\end{itemize}
\enresubsection
\resubsection{Thomson's Problem \hspace*{10pt} \href{https://github.com/omshii/ThomsonProblem}{github.com/omshii/ThomsonProblem}}{}
\begin{itemize} \vspace{-5pt} \itemsep -2pt
	\item Collaborated in a team of three to create a highly optimized and accurate simulation of the Thomson’s problem in physics using Python and numpy. 
\end{itemize}
\enresection

\resection{Honors}
\resubsection{Alumni Memorial Scholar, Colgate University}{Dec 2019}
\begin{itemize} \vspace{-5pt} \itemsep -2pt
	\item Highest honor awarded to incoming freshmen at Colgate, including a 6000\$ research grant
\end{itemize}
\enresubsection
\resubsection{Grand Prize Winner, Google Code-In }{Jun 2018}
\begin{itemize} \vspace{-5pt} \itemsep -2pt
	\item One of 50 winners worldwide out of 3000+ participants in the programming competition.
	\item Visited the Google Headquarters, attended some very interesting talks on topics ranging from cryptography to self-driving cars.
\end{itemize}
\enresection

\end{document}
